\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{xcolor}

% Define Brand Colors
\definecolor{brandTeal}{HTML}{14b8a6}
\definecolor{brandGray}{HTML}{0f172a}
\definecolor{brandRose}{HTML}{f43f5e}

% Geometry setup
\geometry{
    left=25mm,
    right=25mm,
    top=25mm,
    bottom=25mm,
}

% Header and Footer
\pagestyle{fancy}
\fancyhf{}
\lhead{\textcolor{brandTeal}{\textbf{LandlordPro SRS}}}
\rhead{\today}
\cfoot{\thepage}

% Title Formatting
\titleformat{\section}
{\color{brandTeal}\normalfont\Large\bfseries}
{\thesection}{1em}{}

\titleformat{\subsection}
{\color{brandGray}\normalfont\large\bfseries}
{\thesubsection}{1em}{}

% Title Page
\title{\textcolor{brandTeal}{\textbf{Software Requirements Specification}}\\for\\LandlordPro}
\author{LandlordPro Team}
\date{\today}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

\section{Introduction}

\subsection{Purpose}
The purpose of this Software Requirements Specification (SRS) is to describe the functional and non-functional requirements for the \textbf{LandlordPro} property management system. This document is intended for the development team, stakeholders, and quality assurance testers to understand the system's scope and functionality.

\subsection{Scope}
LandlordPro is a full-stack web application designed to empower property managers and administrators to efficiently manage real estate assets. The system provides tools for:
\begin{itemize}
    \item Managing properties, floors, and specific locals (units).
    \item Tracking tenant information and lease agreements.
    \item Recording and monitoring rent payments and property expenses.
    \item Generating reports for financial and operational insights.
    \item Providing role-based access for Admins and Managers.
\end{itemize}

\subsection{Definitions and Acronyms}
\begin{itemize}
    \item \textbf{SRS}: Software Requirements Specification
    \item \textbf{JWT}: JSON Web Token (used for secure authentication)
    \item \textbf{Local}: A specific unit within a property (e.g., Apartment 101, Shop B).
    \item \textbf{Manager}: A user responsible for managing assigned properties.
\end{itemize}

\section{Overall Description}

\subsection{Product Perspective}
LandlordPro is a standalone web-based system consisting of:
\begin{itemize}
    \item A **Frontend** application built with React, Vite, and TailwindCSS (v4).
    \item A **Backend** REST API built with Node.js, Express, and Sequelize.
    \item A **Database** layer using PostgreSQL.
\end{itemize}

\subsection{User Classes and Characteristics}
\begin{enumerate}
    \item \textbf{Admin}: Superuser with full system access. Can manage all users (including Managers), properties, settings, and view system-wide reports.
    \item \textbf{Manager}: Property Manager responsible for specific properties. Can manage leases, tenants, payments, and expenses for their assigned properties.
    \item \textbf{Tenant (Non-System User)}: Tenants do not log in. They are entities managed by the system (profiles, lease data, payment history).
\end{enumerate}

\subsection{Operating Environment}
\begin{itemize}
    \item \textbf{Client Side}: Modern web browsers (Chrome, Firefox, Safari, Edge).
    \item \textbf{Server Side}: Docker environment supporting Node.js and PostgreSQL.
\end{itemize}

\section{System Features}

\subsection{Authentication \& Authorization}
\textbf{Description}: Secure user access control.
\begin{itemize}
    \item Users (Admins and Managers) shall be able to login securely.
    \item The system shall use JWT for session management.
    \item Access to routes shall be restricted based on roles (\texttt{/admin/*} vs \texttt{/manager/*}).
\end{itemize}

\subsection{Property Structure Management}
\textbf{Description}: Hierarchical management of assets.
\begin{itemize}
    \item \textbf{Properties}: Top-level assets created with a defined number of floors and optional basement.
    \item \textbf{Auto-Generation}: The system automatically generates the Ground Floor, subsequent floors, and a Basement (if selected) upon property creation.
    \item \textbf{Locals}: Individual rentable units on floors.
    \item Managers shall be able to navigate this hierarchy to manage specific units.
\end{itemize}

\subsection{Tenant \& Lease Management}
\textbf{Description}: Managing relationships.
\begin{itemize}
    \item Managers shall be able to register new tenants (Individuals or Companies).
    \item The system shall track lease agreements (Start Date, End Date, Rent Amount).
    \item The system shall handle lease renewals and terminations.
\end{itemize}

\subsection{Financial Management}
\textbf{Description}: Tracking cash flow.
\begin{itemize}
    \item \textbf{Payments}: Managers shall record rent payments received from tenants.
    \item \textbf{Expenses}: Managers shall log property-related expenses (maintenance, utilities).
    \item \textbf{Payment Modes}: Admins can configure accepted payment methods.
\end{itemize}

\subsection{Reporting}
\textbf{Description}: Business intelligence.
\begin{itemize}
    \item The system shall generate reports on income, expenses, and occupancy rates.
    \item Documents and contracts can be managed within the system.
\end{itemize}

\section{External Interface Requirements}

\subsection{User Interface Design}
The system features a modern, clean aesthetics using a **Teal** and **Gray** color palette.
\begin{itemize}
    \item \textbf{Primary Color}: Teal (\texttt{\#14b8a6}) - Used for actions, highlights, and active states.
    \item \textbf{Secondary Color}: Gray/Slate (\texttt{\#0f172a}) - Used for text, sidebars, and structural elements.
    \item \textbf{Error Color}: Rose (\texttt{\#f43f5e}) - Used for alerts and form errors.
    \item \textbf{Dark Mode}: Fully supported with dark gray backgrounds and adjusted contrast.
\end{itemize}

\section{Non-Functional Requirements}

\subsection{Security}
\begin{itemize}
    \item Passwords must be hashed using Bcrypt.
    \item Role-based middleware must protect all API endpoints.
\end{itemize}

\subsection{Performance}
\begin{itemize}
    \item Dashboard data retrieval should be optimized with database indexing.
    \item The frontend should use code-splitting (Vite) for fast initial load.
\end{itemize}

\end{document}
