\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[none]{hyphenat}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{tcolorbox}
\usepackage{enumitem}

% Define Brand Colors
\definecolor{brandTeal}{HTML}{14b8a6}
\definecolor{brandGray}{HTML}{0f172a}
\definecolor{brandLight}{HTML}{f0fdfa} % Very light teal for boxes

% Geometry setup
\geometry{
    left=25mm,
    right=25mm,
    top=25mm,
    bottom=25mm,
}

% Header and Footer
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{15pt} % Fix headheight warning
\lhead{\textcolor{brandTeal}{\textbf{LandlordPro Customer Manual}}}
\rhead{\thepage}
\cfoot{\small \url{www.landlordpro.rw}}

% Title Formatting
\titleformat{\section}
{\color{brandTeal}\normalfont\Large\bfseries}
{\thesection}{1em}{}

\titleformat{\subsection}
{\color{brandGray}\normalfont\large\bfseries}
{\thesubsection}{1em}{}

% Tip Box
\newtcolorbox{tipbox}{
    colback=brandLight,
    colframe=brandTeal,
    title=\textbf{Pro Tip}, % Removed Unicode emoji
    coltitle=white,
    boxrule=0.5mm
}

% Title Page
\title{
    \vspace{2cm}
    \textcolor{brandTeal}{\textbf{\Huge Welcome to LandlordPro}}\\
    \vspace{0.5cm}
    \textcolor{brandGray}{\Large The Easy Way to Manage Your Properties}\\
    \vspace{2cm}
    \textbf{Customer User Manual}\\
    \small For Version 1.0\\
    \vspace{1cm}
    \url{www.landlordpro.rw}
}
\author{}
\date{\today}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

\section{Welcome Aboard!}
Thank you for choosing **LandlordPro**. We built this system to help you manage your properties, tenants, and payments without the headache of spreadsheets or paperwork. 

This guide is written in plain English to help you get started immediately. No technical skills required!

\section{Getting Started}

\subsection{Logging In}
1. Open your web browser (like Chrome, Safari, or Edge).
2. Type in the address: \textcolor{brandTeal}{\url{www.landlordpro.rw}}
3. Enter your **Email Address** and **Password**.
4. Click the teal **Login** button.

\subsection{Your Dashboard}
Once you log in, you will see your **Dashboard**. Think of this as your "Mission Control".
\begin{enumerate}
    \item **Top Bar**: Shows your profile and notifications.
    \item **Side Menu**: Your main navigation (Properties, Tenants, Payments, etc.).
    \item **Main Area**: 
    \begin{itemize}
        \item **KPI Cards**: Total Properties, Active Leases, and Monthly Inflow.
        \item **Occupancy Matrix**: A pie chart showing occupied vs. available units.
        \item **Performance Velocity**: A graph tracking your payments and new leases over time.
    \end{itemize}
\end{enumerate}

\subsection{Managing Your Profile \& Password}
You can update your personal details and password from the Profile page.
\begin{enumerate}
    \item Click on your **Profile Icon** or name in the sidebar/top bar.
    \item You will see your identity details.
    \item **To Change Password**: Click the button labeled **Security Override**.
    \item Enter your current password and your new password.
    \item Click **Save**.
\end{enumerate}

\begin{tipbox}
    Note: You can only update your password \textbf{after logging in}. If you forget your password, please contact an Administrator or Support to reset it for you.
\end{tipbox}

\section{Managing Your Properties}
Before you can add tenants, you need to tell the system about your buildings.

\subsection{Step 1: Add a Property}
1. Click on **Properties** in the side menu.
2. Click the **+ Add Property** button (usually at the top right).
3. Fill in the simple form:
   \begin{itemize}
       \item **Name**: Give it a nickname (e.g., "Sunrise Apartments").
       \item **Address**: Where is it located?
       \item **Number of Floors**: Enter the total number of floors.
       \item **Has Basement**: Check this box if the building has a basement level.
   \end{itemize}
4. Click **Save**.

\subsection{Step 2: Add Units (Locals)}
The system automatically creates the floors for you based on the number you entered!
1. Click on the property name you just created.
2. You will see the list of floors (e.g., Basement, Ground Floor, Floor 1).
3. Click on a Floor to add a **Local** (Unit).
   \begin{itemize}
       \item **Name/Number**: e.g., "Apt 101" or "Shop B".
       \item **Rent Amount**: How much does this unit cost per month?
   \end{itemize}

\section{Managing Tenants}

\subsection{Adding a New Tenant}
1. Click on **Tenants** in the side menu.
2. Click **Add Tenant**.
3. Choose functionality: **Individual** (a person) or **Company** (a business).
4. Enter their **Name**, **Phone**, and **Email**.
5. Click **Save**.

\subsection{Creating a Lease (Moving them in)}
Now, connect the Tenant to a Unit.
1. Go to the **Leases** tab.
2. Click **New Lease**.
3. Select the **Tenant** from the list.
4. Select the **Property** and **Unit** (Local) they are renting.
5. Set the **Start Date** (when they move in) and **End Date** (optional).
6. Click **Create Lease**.

\subsection{Modifying or Renewing a Lease}
Need to extend a lease or change the rent?
1. In the **Leases** tab, find the tenant.
2. Click the **Edit Icon** (Paper/Pen).
3. Update the **Termination Date** to renew, or change the **Status** to 'Inactive' to end the lease.
4. Click **Save**.

\section{Money Matters}

\subsection{Recording a Rent Payment}
Since your tenants might pay you in cash, bank transfer, or mobile money, you need to record it here so the system tracks it.

1. Click on **Payments** in the side menu.
2. Click **Record Payment**.
3. Select the **Lease** (search by tenant name).
4. Enter the **Amount Paid**.
5. Select the **Payment  Mode** (Cash, Transfer, Check).
6. (Optional) Upload a picture of the receipt or bank slip.
7. Click **Save**.

The system will automatically update the tenant's balance to show they have paid!

\subsection{Tracking Expenses}
Did you pay for plumbing repairs or cleaning? Record it!
1. Click on **Expenses**.
2. Click **Add Expense**.
3. Enter the **Amount** and **Description** (e.g., "Fixed broken tap").
4. Link it to the Property so you know which building is costing you money.
5. Click **Save**.

\section{Reports \& Analytics}
You can generate PDF reports for your records.
\begin{enumerate}
    \item Go to the **Leases** tab.
    \item Click the **Generate Analytics** button (top right).
    \item The system will download a PDF summary of your lease portfolio and status.
\end{enumerate}

\section{Need Help?}
If you ever get stuck, send a whatsapp message on 0783165626.

\vspace{1cm}
\begin{center}
    \textcolor{brandGray}{\textit{LandlordPro - Making Property Management Simple.}}
\end{center}

\end{document}
